Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-08-19 Scripts/Initial_Analysis.Rmd
All figures created. Next: Stats

#### Data Needed for Analysis

@@

@@

# Prepare data from results
Data <- Prop_results %>% 
  # get coords for sources
  left_join(Eez_centroid_eck,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  left_join(Eez_centroid_eck,
            by = "eez_name") %>% 
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_early = ifelse(is.na(per_early_plot),0,per_early_plot),
    per_mid = ifelse(is.na(per_mid_plot),0,per_mid_plot)
  ) %>% 
  drop_na() %>%
  filter(
    variable == "mean_eez"#,
    # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

@@

# Create data path for line connections
paths <- network_data_sf %>% 
  sf::st_set_geometry(NULL) %>% 
  unnest() %>% 
  mutate_at(vars(X,Y), round,2) %>% 
  gather("time_step","per_chng",per_mid_plot:per_early_plot)

@@

Data <- Data %>% 
  gather("time_step","per_chng",per_mid_plot:per_early_plot)

@@

time <- "per_mid_plot"
# time <- "per_early_plot"

@@

Prop_map <- ggplot() +
  geom_sf(data = subset(World_map, sovereignt != "Antarctica"), size = 0.1, fill = "gray50", col = "gray50") +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
  geom_point(data = subset(Data, time_step == time & per_chng < 0),
             aes(start_lon,
                 start_lat,
                 col = per_chng),
             size = 0.05,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(paths, time_step == time & per_chng > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_chng
            ),
            size = 0.3,
            arrow = arrow(length = unit(0.009, "npc"),
                          ends = "first"),
            show.legend = NA) +
  my_ggtheme_m() +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Data$per_chng)),
    breaks = seq(0,max(Data$per_chng),5),
    # option="magma",
    # direction = -1
  ) +
  ggsave("./Figures/figS1a.png",
  width = 10,
  height = 6,
  units = "in"
  )

@@

Lat_am_eez %>% filter(str_detect(sf_eez_name,"Tri"))

Lat_am_data <- Data %>% 
  filter(source %in% Lat_am_eez$sf_eez_name)

@@

Lat_am_map <- ggplot() +
  geom_sf(data = Lat_am_eez, size = 0.1, fill = "white", col = "gray30") +
  geom_sf(data = Lat_am_land, size = 0.1, fill = "gray50", col = "gray40") +
  geom_point(data = subset(Lat_am_data, time_step == time & per_chng < 0 ),
             aes(start_lon,
                 start_lat,
                 col = per_chng),
             size = 1,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(Lat_am_paths, time_step == time & per_chng > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_chng
            ),
            size = 1,
            arrow = arrow(length = unit(0.05, "npc"),
                          ends = "first"),
            show.legend = NA) +
  coord_sf(xlim = c(-100, -55),ylim = c(9, 30)) + 
  labs(x = "Lon", y = "Lat") +
  scale_x_continuous(breaks = seq(-100,60,10)) +
  scale_y_continuous(breaks = seq(10,30,5)) +
  # my_ggtheme_m() +
  theme(legend.position = "",
        panel.background = element_rect(fill = "white")) +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Lat_am_data$per_chng)),
    breaks = seq(0,max(Lat_am_data$per_chng),5),
    # option="magma",
    # direction = -1
  );Lat_am_map

@@

# Med data
Med_data <- Data %>% 
  filter(source %in% Med_eez$sf_eez_name)

@@

# Med plot
Med_map <- ggplot() +
  geom_sf(data = Med_eez, size = 0.5, fill = "white", col = "gray30") +
  geom_sf(data = Med_land, size = 0.5, fill = "gray50", col = "gray40") +
  geom_point(data = subset(Med_data, time_step == time & per_chng < 0 ),
             aes(start_lon,
                 start_lat,
                 col = per_chng),
             size = 1,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(Med_paths, time_step == time & per_chng > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_chng
            ),
            size = 1,
            arrow = arrow(length = unit(0.05, "npc"),
                          ends = "first"),
            show.legend = NA) +
  coord_sf(xlim = c(-3, 35),ylim = c(30, 45)) +
  labs(x = "Lon", y = "Lat") +
  scale_x_continuous(breaks = seq(-5,35,10)) +
  scale_y_continuous(breaks = seq(30,50,5)) +
  # my_ggtheme_m() +
  theme(legend.position = "",
        panel.background = element_rect(fill = "white")) +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Med_data$per_chng)),
    breaks = seq(0,max(Med_data$per_chng),5),
    # option="magma",
    # direction = -1
  );Med_map

@@

Eu_eez %>% filter(str_detect(sf_eez_name,"Romania"))

Eu_data <- Data %>% 
  filter(source %in% Eu_eez$sf_eez_name)

@@

Eu_map <- ggplot() +
  geom_sf(data = Eu_eez, size = 0.5, fill = "white", col = "gray30") +
  geom_sf(data = Eu_land, size = 0.5, fill = "gray50", col = "gray40") +
  geom_point(data = subset(Med_data, time_step == time & per_chng < 0 ),
             aes(start_lon,
                 start_lat,
                 col = per_chng),
             size = 1,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(Eu_paths, time_step == time & per_chng > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_chng
            ),
            size = 1,
            arrow = arrow(length = unit(0.05, "npc"),
                          ends = "first"),
            show.legend = NA) +
  coord_sf(xlim = c(-15, 30), ylim = c(45, 65)) +
  labs(x = "Lon", y = "Lat") +
  scale_y_continuous(breaks = seq(45,65,10)) +
  # scale_x_continuous(breaks = seq(45,65,10)) +
  # my_ggtheme_m() +
  theme(legend.position = "",
        panel.background = element_rect(fill = "white", color = "white"),
        panel.grid.major =  element_line(color = "white")
        ) +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Eu_data$per_chng)),
    breaks = seq(0,max(Eu_data$per_chng),5),
    # option="magma",
    # direction = -1
  );Eu_map

@@

>>>>

#### Read Data for Analysis

@@

# Species depth clasification

Spp_depth <-fread(paste(my_path("D"),"SAU/SppTaxonName.csv", sep ="")) %>% 
  clean_names()

@@

# Prepare data from results
Data <- Prop_results %>% 
  # get coords for sources
  left_join(Eez_centroid_eck,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  left_join(Eez_centroid_eck,
            by = "eez_name") %>% 
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_early = ifelse(is.na(per_early),0,per_early),
    per_mid = ifelse(is.na(per_mid),0,per_mid)
  ) %>% 
  drop_na() %>%
  filter(
    variable %in% c("mean_eez","n_spp")#,
    # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

@@

# Create data path for line connections
paths <- network_data_sf %>% 
  sf::st_set_geometry(NULL) %>% 
  unnest() %>% 
  mutate_at(vars(X,Y), round,2) %>% 
  gather("time_step","per_chng",per_early:per_mid) %>% 
  mutate(per_plot = ifelse(per_chng > 100,100,per_chng))

@@

# Proportion map data 
Map_data <- Data %>% 
  gather("time_step","per_chng",per_early:per_mid) %>% 
  mutate(per_plot = ifelse(per_chng > 100,100,per_chng))

# Average number of taxa to change per eez

n_taxa_data <- Prop_results %>% 
  filter(variable == "n_spp") %>% 
  rename(sf_eez_name = eez_name) %>% 
  left_join(Matching_names) %>% 
  group_by(sau_fishing_entity,fishing_entity_id) %>% 
  summarise(total_spp = mean(early,na.rm=T))

n_taxa_map <- World_map %>% 
  left_join(n_taxa_data,
            by = c("sau_fishing_entity","fishing_entity_id")
            )

@@

# time <- "per_mid_plot"
time <- "per_early"

@@

Prop_map <- ggplot() +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = total_spp),
          size = 0.1,col = "white") +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
  geom_point(data = subset(Map_data, time_step == time & per_plot < 0),
             aes(start_lon,
                 start_lat,
                 col = per_plot),
             size = 0.05,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(paths, time_step == time & per_plot > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_plot
            ),
            size = 0.3,
            arrow = arrow(length = unit(0.008, "npc"),
                          ends = "first"),
            show.legend = NA) +
  my_ggtheme_m() +
  scale_colour_viridis(
    name="Average Gain of Stock-Share Ratio (%)\nand Number of taxa (n)",
    limits = c(0,max(Map_data$per_plot)),
    breaks = seq(0,max(Map_data$per_plot),10),
    # option="magma",
    # direction = -1
  ) +
  scale_fill_viridis(
    name="Average Gain of Stock-Share Ratio (%)\nand Number of taxa (n)",
    limits = c(0,max(Map_data$per_plot)),
    breaks = seq(0,max(Map_data$per_plot),10),
    alpha = 0.8
    # option="magma",
    # direction = -1
  ) +
  ggsave("./Figures/fig2ax.png",
  width = 12,
  height = 8,
  units = "in"
  )

@@

# Lat_am_eez %>% filter(str_detect(sf_eez_name,"Tri"))

Lat_am_data <- Map_data %>% 
  filter(source %in% Lat_am_eez$sf_eez_name)

@@

Lat_am_map <- ggplot() +
  geom_sf(data = Lat_am_eez, size = 0.1, fill = "white", col = "gray30") +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = total_spp),
          size = 0.1,col = "white") +
  geom_point(data = subset(Lat_am_data, time_step == time & per_plot < 0 ),
             aes(start_lon,
                 start_lat,
                 col = per_plot),
             size = 1,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(Lat_am_paths, time_step == time & per_plot > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_plot
            ),
            size = 1,
            arrow = arrow(length = unit(0.05, "npc"),
                          ends = "first"),
            show.legend = NA) +
  coord_sf(xlim = c(-100, -55),ylim = c(9, 30)) + 
  labs(x = "Lon", y = "Lat") +
  scale_x_continuous(breaks = seq(-100,60,10)) +
  scale_y_continuous(breaks = seq(10,30,5)) +
  # my_ggtheme_m() +
  theme(legend.position = "",
        panel.background = element_rect(fill = "white", color = "white"),
        panel.grid.major =  element_line(color = "white")
        ) +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Lat_am_data$per_plot)),
    breaks = seq(0,max(Lat_am_data$per_plot),10),
    # option="magma",
    # direction = -1
  )+
  scale_fill_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Lat_am_data$per_plot)),
    breaks = seq(0,max(Lat_am_data$per_plot),10),
    # option="magma",
    # direction = -1
  );Lat_am_map

@@

# Med data
Med_data <- Map_data %>% 
  filter(source %in% Med_eez$sf_eez_name)

@@

# Med plot
Med_map <- ggplot() +
  geom_sf(data = Med_eez, size = 0.5, fill = "white", col = "gray30") +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = total_spp),
          size = 0.1,col = "white") +
  geom_point(data = subset(Med_data, time_step == time & per_plot < 0 ),
             aes(start_lon,
                 start_lat,
                 col = per_plot),
             size = 1,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(Med_paths, time_step == time & per_plot > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_plot
            ),
            size = 1,
            arrow = arrow(length = unit(0.05, "npc"),
                          ends = "first"),
            show.legend = NA) +
  coord_sf(xlim = c(-3, 35),ylim = c(30, 45)) +
  labs(x = "Lon", y = "Lat") +
  scale_x_continuous(breaks = seq(-5,35,10)) +
  scale_y_continuous(breaks = seq(30,50,5)) +
  # my_ggtheme_m() +
  theme(legend.position = "",
        panel.background = element_rect(fill = "white", color = "white"),
        panel.grid.major =  element_line(color = "white")
        ) +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Med_data$per_plot)),
    breaks = seq(0,max(Med_data$per_plot),5),
    # option="magma",
    # direction = -1
  )+
  scale_fill_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Med_data$per_plot)),
    breaks = seq(0,max(Med_data$per_plot),5),
    # option="magma",
    # direction = -1
  );Med_map

@@

# Eu_eez %>% filter(str_detect(sf_eez_name,"Romania"))

Eu_data <- Map_data %>% 
  filter(source %in% Eu_eez$sf_eez_name)

@@

Eu_map <- ggplot() +
  geom_sf(data = Eu_eez, size = 0.5, fill = "white", col = "gray30") +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = total_spp),
          size = 0.1,col = "white") +
  geom_point(data = subset(Med_data, time_step == time & per_plot < 0 ),
             aes(start_lon,
                 start_lat,
                 col = per_plot),
             size = 1,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(Eu_paths, time_step == time & per_plot > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_plot
            ),
            size = 1,
            arrow = arrow(length = unit(0.05, "npc"),
                          ends = "first"),
            show.legend = NA) +
  coord_sf(xlim = c(-15, 30), ylim = c(45, 65)) +
  labs(x = "Lon", y = "Lat") +
  scale_y_continuous(breaks = seq(45,65,10)) +
  # scale_x_continuous(breaks = seq(45,65,10)) +
  # my_ggtheme_m() +
  theme(legend.position = "",
        panel.background = element_rect(fill = "white", color = "white"),
        panel.grid.major =  element_line(color = "white")
        ) +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Eu_data$per_plot)),
    breaks = seq(0,max(Eu_data$per_plot),5),
    # option="magma",
    # direction = -1
   )+
  scale_fill_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Med_data$per_plot)),
    breaks = seq(0,max(Med_data$per_plot),5),
    # option="magma",
    # direction = -1
  );Eu_map

@@

### Species level analysis

#### Demersal Vs Pelagic

```{r deme_pela, eval = F, echo =F}

Dem_pel <- Eme_Res %>% 
  filter(tresh == "Tresh_one",
         !is.na(un_sub_region)) %>% 
  left_join(Spp_depth)

Dem_pel_mean <- Dem_pel %>% 
  group_by(dem_pel) %>% 
  summarise(mean  = mean(emerging_yr))

ggplot(Dem_pel) +
  geom_boxplot(
    aes(
      x = reorder(dem_pel,emerging_yr),
      y = emerging_yr,
      fill = un_sub_region
    )
  ) +
  geom_line(data = Dem_pel_mean,
    aes(
      x = dem_pel,
      y = mean
    )
)

ggplot(Dem_pel) +
  geom_boxplot(
    aes(
      x = reorder(dem_pel,emerging_yr),
      y = emerging_yr
    )
  ) +
  facet_wrap(~un_sub_region)
